Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-07-01 review_article.Rmd
Cartogram figures

!["A choropleth map of the United States of America. Each state is coloured according the the average of the 20"](figures/ggchoro.png)

@@

< Figure 2 here - basic cartogram - easy to see >

@@

@@

Dorling -@ACTUC puts forward a simple question:
>If, for instance, it is desirable that areas on a map have boundaries which are as simple as possible, why not draw the areas as simple shapes in the first place?

>>>>

!["A choropleth map of the United States of America."](figures/ggchoro.png)

@@

@@

!["A contiguous cartogram of the Unites States of America"](figures/ggcont.png)

@@

!["A Non - contiguous cartogram of the Unites States of America"](figures/ggncont.png)

!["A dorling cartogram of the Unites States of America"](figures/ggdorl.png)

Dorling -@ACTUC puts forward a simple question:

>If, for instance, it is desirable that areas on a map have boundaries which are as simple as possible, why not draw the areas as simple shapes in the first place?
